---
title: "Data Wrangling: Getting your hands dirty"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Getting your hands dirty 1

Let's begin with the first part of this exercise!

* Step 1 : Import via a csv

Import the csv file called chapter6data.csv.

```{r}
library(readr)
gdp <-
```

* Step 2 : Import via a gsheet

Import a dataset containing longitude and latitude from this gsheet: https://docs.google.com/spreadsheets/d/1nehKEBKTQx11LZuo5ZJFKTVS0p5y1ysMPSOSX_m8dS8/edit?usp=sharing

```{r}
library(gsheet)
locations <-
```

# Getting your hands dirty 2

Let's begin with the second part of this exercise:

* Step 3 : Delete the column

Delete the column X1 of the gdpdata frame.

```{r}

```

* Step 4 : Filter the data

Filter the gdpdata frame to only keep the following countries: "United States", "Canada", "Japan", "Belgium" and "France".

```{r}
library(dplyr)
gdp2 <-
```

# Getting your hands dirty 3

Let's begin with the third part of this exercise:

* Step 5 : "Lengthens" the data

You need to "lengthens" (modify from wide to long) the dataframe "gdp2" to get three column: "country", "year", "gdp".

```{r}
library(tidyr)
gdp3 <-
```


# Getting your hands dirty 4

Now, let's begin with the last part of this exercise:

Step 6 : Merging datasets
Join the data frame locations to the data frame gdp3.

gdp4 <-
